A game theoretic model of the behavioural gaming that takes place at the EMS - ED interface\tnoteref{t1}

### 2022-03-26 sections/queueing_model/blocking_time/main.tex
Add sentence to explain reason behind figures 4-6
Address several todos
Update plots in paper to illustarte the truncation

Figure \ref{fig:markov_vs_des_blocking_time_comparison} illustrates a comparison 
between the formulas that arise from the Markov chain model and the equivalent 
values of the blocking time extracted from discrete event simulation
(appendix~\ref{sec:appendix_des}).
The blocking time is calculated using both methods for a range of values of
\(\lambda_2\).
The simulation was ran 100 times and the recorded mean blocking time at each 
iteration is used to populate the violin plots.
It can be seen that the blocking times generated by the simulation match the
ones generated by the Markov chains model.

\begin{figure}[H]
    \centering
    \includegraphics[width=.8\textwidth]{imgs/blocking_time_comparison/blocking.pdf}
    \caption{
        Comparison of mean blocking time between values obtained from the 
        Markov chain formulas and values obtained from simulation.
    }
    \label{fig:markov_vs_des_blocking_time_comparison}
\end{figure}

>>>>

Figure \ref{fig:markov_vs_des_blocking_time_comparison} illustrates a comparison 
between the formulas that arise from the Markov chain model and the equivalent 
values of the blocking time extracted from discrete event simulation
(appendix~\ref{sec:appendix_des}).
The blocking time is calculated using both methods for a range of values of
\(\lambda_2\).
The figure is used to demonstrate the accuracy of the blocking time formula of
the constructed queueing model as well as the effect of truncating the model.
The simulation was ran 100 times and the recorded mean blocking time at each 
iteration is used to populate the violin plots.
Similar to figure \ref{fig:markov_vs_des_waiting_time_comparison_overall}, these
plots shows a comparison between the calculated mean blocking time using Markov 
chain, using a truncated simulation and using a simulation with infinite
capacity (without the artificial parameters \(N\) and \(M\)).
The blocking times generated by the truncated simulation match the ones
generated by the Markov chains model.
Note that this comparison includes just type 2 individuals since type 1 
individuals cannot be blocked.

\begin{figure}[H]
    \centering
    \includegraphics[width=\textwidth]{imgs/truncation_effect/blocking/main.pdf}
    \caption{
        Comparison of mean blocking time between values obtained from the Markov 
        chain formula, values obtained from the truncated simulation and values
        obtained from the untruncated simulation.
    }
    \label{fig:markov_vs_des_blocking_time_comparison}
\end{figure}

### 2022-03-26 sections/queueing_model/proportion_within_target/main.tex
Add sentence to explain reason behind figures 4-6
Update plots in paper to illustarte the truncation

Figure \ref{fig:markov_vs_des_proportion_comparison_overall} shows a comparison
of the mean proportion of individuals within target when using Markov chains 
and discrete event simulation (appendix~\ref{sec:appendix_des}).
The simulation was ran 100 times and the recorded proportions at each iteration 
is used to populate the violin plots.
The proportions generated by the simulation match the ones generated by the 
Markov chains model.
Note that this comparison includes both type 1 and type 2 individuals.
A separate comparison of only type 1 and only type 2 individuals can be found 
in appendix~\ref{sec:appendix_additional_figures}.

\begin{figure}[H]
    \centering
    \includegraphics[width=.8\textwidth]{imgs/proportion_within_target_comparison/proportion_overall.pdf}
    \caption{
        Comparison of proportion within target time for both type of 
        individuals between values obtained from the Markov chain formulas 
        and values obtained from simulation. 
    }
    \label{fig:markov_vs_des_proportion_comparison_overall}
\end{figure}

>>>>

Figure \ref{fig:markov_vs_des_proportion_comparison_overall} shows a comparison
of the mean proportion of individuals within target when using Markov chains 
and discrete event simulation (appendix~\ref{sec:appendix_des}).
The figure is used to demonstrate the accuracy of the formula for the 
proportion of individuals within time of the constructed queueing model
as well as the effect that truncating the model has on the formula.
The simulation was ran 100 times and the recorded proportions at each iteration 
is used to populate the violin plots.
Similar to figures \ref{fig:markov_vs_des_waiting_time_comparison_overall} and
\ref{fig:markov_vs_des_blocking_time_comparison}, these plots shows a comparison
between the calculated mean proportion of individuals within time using Markov 
chain, using a truncated simulation and using a simulation with infinite
capacity (without the artificial parameters \(N\) and \(M\)).
The proportions generated by the truncated simulation match the ones generated
by the Markov chains model.
Note that this comparison includes both type 1 and type 2 individuals.
A separate comparison of only type 1 and only type 2 individuals can be found 
in appendix~\ref{sec:appendix_additional_figures}.

\begin{figure}[H]
    \centering
    \includegraphics[width=\textwidth]{imgs/truncation_effect/proportion/main.pdf}
    \caption{
        Comparison of mean proportion of individuals within target time between 
        values obtained from the Markov chain formula, values obtained from the
        truncated simulation and values obtained from the untruncated
        simulation. 
    }
    \label{fig:markov_vs_des_proportion_comparison_overall}
\end{figure}

### 2022-03-26 sections/queueing_model/waiting_time/main.tex
Update plots in paper to illustarte the truncation

Figure \ref{fig:markov_vs_des_waiting_time_comparison_overall} shows a 
comparison between the calculated mean waiting time using Markov chains and the
simulated waiting time using discrete event simulation over a range of values of 
\(\lambda_2\) (details of the discrete event simulation model are given in 
appendix~\ref{sec:appendix_des}).
The figure is used to demonstrate the accuracy of the waiting time formula of
the constructed queueing model.
The simulation was ran 100 times and the recorded mean waiting time at each 
iteration is used to populate the violin plots.
The waiting times generated by the simulation match the ones generated by the 
Markov chains model.
Note that this comparison includes both type 1 and type 2 individuals.
A separate comparison of only type 1 and only type 2 individuals can be found 
in appendix~\ref{sec:appendix_additional_figures}.

\begin{figure}[H]
    \centering
    \includegraphics[width=.8\textwidth]{imgs/waiting_time_comparison/waiting_overall.pdf}
    \caption{
        Comparison of mean waiting time for both types of individuals between 
        values obtained from the Markov chain formulas and values obtained from 
        simulation.
    }
    \label{fig:markov_vs_des_waiting_time_comparison_overall}
\end{figure}

>>>>

Figure \ref{fig:markov_vs_des_waiting_time_comparison_overall} shows a 
comparison between the calculated mean waiting time using Markov chains and the
simulated waiting time using discrete event simulation over a range of values of 
\(\lambda_2\) (details of the discrete event simulation model are given in 
appendix~\ref{sec:appendix_des}).
The figure is used to demonstrate the accuracy of the waiting time formula of
the constructed queueing model as well as the effect of truncating the model.
The simulation was ran 100 times and the recorded mean waiting time at each 
iteration is used to populate the violin plots.
In detail, figure \ref{fig:markov_vs_des_waiting_time_comparison_overall} shows
the calculated mean waiting time using Markov chain, using a truncated 
simulation and using a simulation with infinite capacity (without the artificial
parameters \(N\) and \(M\)).
Each plot corresponds to different values of \(N\) and \(M\) and is ran over 
different values of \(\lambda_2\).
The untruncated simulation values (blue) are the same at all three graphs since
the effect of truncation does not apply to it.
The waiting times generated by the truncated simulation match the ones generated 
by the Markov chains model.
Note that this comparison includes both type 1 and type 2 individuals.
A separate comparison of only type 1 and only type 2 individuals can be found 
in appendix~\ref{sec:appendix_additional_figures}.

\begin{figure}[H]
    \centering
    \includegraphics[width=\textwidth]{imgs/truncation_effect/waiting/main.pdf}
    \caption{
        Comparison of mean waiting time between values obtained from the Markov 
        chain formula, values obtained from the truncated simulation and values
        obtained from the untruncated simulation.
    }
    \label{fig:markov_vs_des_waiting_time_comparison_overall}
\end{figure}
